R Notebook

### 2019-11-10 src/plots for paper.Rmd
updates to the testing file

permelt <- melt(permu, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") +  scale_fill_viridis_d(direction = 1) + theme_half_open(12) + 
png("../output/maxent/paper_plots/permutation_plot.png")
print(perpl)
dev.off()
```

>>>>

mthna <- c("Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")

permelt <- melt(permu, id = "Month") #need to melt the data into this format for ggplot
perpl <- ggplot(data = permelt, aes(x = Month, y = value, fill = variable)) + geom_bar(stat = "identity") +  scale_fill_viridis_d(direction = 1) + theme_half_open(12) + scale_x_discrete(limits = mthna) + labs(y = "Permutation Importance (%)")
png("../output/maxent/paper_plots/permutation_plot.png")
print(perpl)
dev.off()
```

### 2019-11-10 src/testing_file.Rmd
updates to the testing file

# and get it as a proportion of habitat maybe....

@@

>>>>

# map with nafo zons and mcp

```{r}
library(ggplot2)
library(raster)

outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis - aea proj
nafo <- shapefile("../data/bio/nafo_zones/nafo_zones_wgs84.shp") #in wgs proj
aea <- raster("../output/env/aea.tif") #the correct projections
nafoa <- spTransform(nafo, crs(aea)) # nafo to aea
labels <- layer(sp.text(coo))
land <- shapefile("../data/env/landp/landpro.shp") #made in arcgis - aea proj

nafoaf <- fortify(nafoa, regions = "ZONE")

ggplot(nafoa) + aes() + geom_polygon()

@@

#env plots - variable over depth by month

```{r}
library(ggplot2)
library(reshape2)

presab <- read.csv("../output/bio/presab_nafo_yr.csv", header = TRUE)
background <- subset(presab, occurrence == "0")
background$month <- as.factor(background$month)
background <- subset(background, select = c(month, temp_depth, depth_layer, decimalLongitude, decimalLatitude))
dl <- unique(background$depth_layer)
dl <- sort(dl)
test <- subset(background, month == "3")

ggplot(test, aes(x = temp_depth, y = decimalLatitude)) + geom_point() # aes(color = month, group = month)
plot(background)

#amo boxplots?

```{r}
amoraw <- read.csv("../data/env/amon.us.data.csv", header = TRUE) 
colnames(amoraw) <- c("year", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
amo <- amoraw[amoraw$year >= 1996, ]
amo <- subset(amo, select = -c(year))
amo2 <- melt(amo, value.name = "value")
amo2$variable <- as.integer(amo2$variable)

boxplot(amo2$value ~ amo2$variable)
